{\helveticaitalic{Supplementary Material}}

### 2021-12-29 bbbq_article.tex
Reword sentence, thanks Frans

In our experiment, we define a TMH-derived epitope as a peptide that overlaps
with a TMH for at least one amino acid. 
One could argue that we should use a higher number of overlapping amino acids, so that the epitope has a higher TMH coverage.
We chose not too, for two reason: (1) epitopes that overlap with a TMH
for 1 AA already, cannot be processed by the proteasome in a known and conventional
way (2) whatever number of overlapping amino acids we use, we expect the pattern to be the same.
However, using only 1 AA gives the most TMH-derived epitopes and hence the highest statistical
power.

>>>>

In our experiment, we define a TMH-derived epitope as a peptide that overlaps
with a TMH for at least one amino acid. 
One could argue that we should use a higher number of overlapping amino acids, so that the epitope has a higher TMH coverage.
We chose not to, for two reason: (1) epitopes that overlap
with a TMH for 1 AA already, cannot be processed by the proteasome in a known and conventional way as it still requires extraction from the membrane
(2) whatever number of overlapping amino acids we use, we expect the pattern to be the same as the chance that an epitope stems from a TMH is equally reduced.
However, using only 1 AA gives the most TMH-derived epitopes and hence the highest statistical
power.
